\section{Reviewer 2}

\subsection{Main concerns}

\begin{itemize}
    \item \comm{Definition 2.1 combines function value residuals and gradient norms under a single tolerance $\epsilon$. Since these two measures usually operate on different scales and orders of magnitude, a unified $\epsilon$ may not be well-defined for all problems. The authors should justify the use of this combined stopping criterion or discuss the implications of the scale mismatch between $f(x)-f^*$ and $\|\nabla f(x)\|$.}

    \item \comm{In the pseudocode for both Algorithm 1 and Algorithm 2, the main iteration loop is defined as ``for $k=0,1,\ldots,K_\epsilon$.'' However, as the complexity analysis demonstrates, $K_\epsilon$ depends on unknown constants such as the initial distance to the optimum, $D_0=\|x_0-x^*\|$. Since $D_0$ is unknown a priori, $K_\epsilon$ cannot be used as a practical limit for the total number of iterations. For the sake of clarity, the authors should explicitly define the verifiable stopping criteria, e.g., $\|\nabla f(x_k)\|\le \epsilon$, that would be used in a numerical implementation to trigger the termination of the loop.}

          \resp{Thank you for the valuable insight. We assume that these two questions are closely related thus we answer them together. We have now revised the Definition 2.1. The two tolerances $\epsilon_f$ and $\epsilon_g$ are kept separate because
              the function-value residual $f(x)-f^*$ and the gradient norm
              $\|\nabla f(x)\|$ generally have different scales as you said. Under the bounded hessian assumption and convexity, the two
              measures are related by
              \[
                  \frac{1}{2\kappa_H}\|\nabla f(x)\|^2
                  \leq f(x)-f^*.
              \]
              Hence an $\epsilon_f$-function-value solution is also a
              $\sqrt{2\kappa_H\epsilon_f}$-first-order stationary solution. Conversely,
              under local strong convexity, a sufficiently small gradient norm also
              controls the local function-value residual.\\
              In particular, the
              algorithms below use only the verifiable first-order condition
              $\|\nabla f(x)\|\leq \epsilon_g$ as a stopping criterion. The tolerance $\epsilon_f$ is introduced only for complexity analysis and is reported as an anytime guarantee. It is not used as an input or stopping rule in the algorithm.
          }
\end{itemize}

\subsection{Discussion points}

\begin{itemize}
    \item \comm{Given that trust-region methods naturally handle negative curvature, it would be interesting to hear the authors' views on whether the $\trp$ oracle and estimating sequence techniques could be extended to non-convex settings to find second-order stationary points. Specifically, could such an extension potentially improve upon the complexity bounds of existing unaccelerated non-convex trust-region methods?}

          \resp{We thank the reviewer for this insightful question. Trust-region methods are indeed naturally suited to nonconvex problems because the trust-region subproblem can exploit negative curvature. $\trp$ oracle framework can be used to find second-order stationary points in nonconvex optimization, see~\citet{jiang2026beyond}. That said, combining it with estimating sequence is not immediate. In the convex setting, the estimating-sequence argument relies crucially on global convexity, since affine lower models of $f$ are used to maintain the estimate-sequence inequalities. This mechanism breaks down in general nonconvex problems. We expect it to be useful only under additional structural assumptions, such as higher-order smoothness, controlled nonconvexity, or other conditions that allow suitable surrogate lower models to be constructed~(like the paper~\citet{carmon2017convex} did under second-order smoothness).\\
              Regarding complexity, \citet{carmon2020lower} established a lower bound of order
              \[
                  \Omega\!\left(\sqrt{M}\,(f(x_0)-f^*)\,\epsilon^{-3/2}\right)
              \]
              for finding first-order stationary points using second-order information under Hessian Lipschitz continuity. To the best of our knowledge, among trust-region-type methods, \citet{hamad2022consistently} matches this bound up to absolute constants. However, their guarantee is for first-order stationarity and does not directly provide an approximate second-order stationary point. Other trust-region-type methods can find approximate second-order stationary points, such as those in
              \citet{jiang2026beyond,curtis2017trust,curtis2021trust}, but their complexity guarantees typically involve additional dependencies or less streamlined bounds.\\
              Our view is that it may be possible to design a trust-region-type method that both matches the optimal first-order complexity order and returns an approximate second-order stationary point, but doing so would be highly nontrivial. Moreover, the estimating-sequence technique by itself is unlikely to yield an acceleration benefit in fully general nonconvex problems, because the extra dependency in complexity results is more likely a trust-region-method-related problem.}

    \item \comm{The theoretical guarantees for the $\trp$ oracle rely on exact primal-dual solutions. In large-scale settings, these are typically solved inexactly via iterative methods, e.g., Krylov methods or truncated conjugate gradient methods. Could the authors clarify whether the estimating sequence in Algorithm 1 and the $\lambda=0$ local detection trigger remain robust under relative inexactness? It would be useful to know if the $\widetilde{O}(\epsilon^{-1/3})$ complexity bound is preserved under these conditions.}

          \resp{Thank you for the great question. The estimating-sequence argument is robust to a controlled inexact solution
              of the \(\trp\) subproblem.
                  {\bf To be rigorous, we present the analysis here to briefly demonstrate how to incorporate the inexact solution into the analysis. }
              We describe the global part below, and the local
              detection trigger can be made robust by an additional thresholding rule, and
              we discuss it separately.\\
              At the \(k\)-th iteration, the \(\trp\) subproblem is solved at the point
              \(y_k\). Let
              \[
                  g_k:=\nabla f(y_k),
                  \qquad
                  H_k:=\nabla^2 f(y_k),
                  \qquad
                  \mu_k:=\sigma_k+\lambda_k.
              \]
              We consider an inexact primal-dual pair \((d_k,\lambda_k)\) satisfying the
              following conditions, similar in spirit to~\citet[Equation~(6)]{hamad2022consistently}:
              for some constants
              \(
              \gamma_1\in\left[0,\frac12\right), \gamma_2\in(0,1],
              \)
              we require
              \begin{align}
                  \label{eq.opt-inexact-fo}
                  \|g_k+(H_k+\sigma_k I+\lambda_k I)d_k\|
                          & \leq \gamma_1 M\|d_k\|^2, \\
                  \label{eq.opt-inexact-primal}
                  \|d_k\| & \leq r_k,                 \\
                  \label{eq.opt-inexact-cs}
                  \gamma_2\lambda_k r_k
                          & \leq \lambda_k \|d_k\|.
              \end{align}
              Here \eqref{eq.opt-inexact-fo} is the relative residual condition,
              \eqref{eq.opt-inexact-primal} and \eqref{eq.opt-inexact-cs} are approximate
              primal feasibility and complementarity.
              \paragraph{Global acceleration} For the global estimating-sequence
              argument, the essential ingredient is the
              ratio bound between \(\mu_k\) and \(\|d_k\|\).\\
              Indeed, when \(\lambda_k>0\), \eqref{eq.opt-inexact-primal} and
              \eqref{eq.opt-inexact-cs} imply
              \[
                  \gamma_2 r_k\le \|d_k\|\le r_k.
              \]
              Using the choice
              \[
                  \sigma_k=Mr_k,
                  \qquad
                  r_k=\frac{1}{\sqrt{2M}}\|g_k\|^{1/2},
              \]
              we have
              \[
                  \mu_k\ge \sigma_k=Mr_k\ge M\|d_k\|.
              \]
              Moreover, by convexity, \(H_k\succeq0\), and hence
              \[
                  \mu_k\|d_k\|
                  \le
                  \|(H_k+\mu_k I)d_k\|.
              \]
              Combining this with \eqref{eq.opt-inexact-fo}, we obtain
              \[
                  \mu_k\|d_k\|
                  \le
                  \|g_k\|+\gamma_1 M\|d_k\|^2.
              \]
              Since \(\|g_k\|=2Mr_k^2\) and \(\|d_k\|\ge \gamma_2 r_k\), it follows that
              \[
                  \mu_k
                  \le
                  \left(\frac{2}{\gamma_2^2}+\gamma_1\right)M\|d_k\|.
              \]
              Thus, for all iterations with \(\lambda_k>0\),
              \begin{equation}
                  \label{eq.inexact-ratio}
                  M\|d_k\|
                  \le
                  \mu_k
                  \le
                  \beta M\|d_k\|,
                  \qquad
                  \beta:=\frac{2}{\gamma_2^2}+\gamma_1.
              \end{equation}
              When \(\lambda_k=0\), one can use the same R\&B step as
              in the exact case, but now with the target interval
              \[
                  M\|d_k\|\le \mu_k\le \beta M\|d_k\|.
              \]
              Therefore, the following inexact version of Lemma~2.3
              is sufficient for the global estimating-sequence proof.\\
              \begin{lemma}
                  \label{lem.inexact-inner-product-g-d}
                  Suppose \(f\) is convex and Assumption~2.1 holds. Let
                  \(x\in\mathbb R^n\), \(d\in\mathbb R^n\), and \(\mu>0\). Suppose that
                  \[
                      \|\nabla f(x)+(\nabla^2 f(x)+\mu I)d\|
                      \le
                      \gamma_1 M\|d\|^2
                  \]
                  for some \(\gamma_1\in[0,1/2)\), and suppose that
                  \[
                      M\|d\|\le \mu\le \beta M\|d\|
                  \]
                  for some \(\beta\ge1\). Define
                  \[
                      \delta:=\frac12+\gamma_1,
                      \qquad
                      \eta:=\frac{1-\delta^2}{2}>0.
                  \]
                  Then
                  \begin{equation}
                      \label{eq.inexact-inner-product-first}
                      \left\langle \nabla f(x+d),-d\right\rangle
                      \ge
                      \frac{\|\nabla f(x+d)\|^2}{2\mu}
                      +
                      \eta\mu\|d\|^2.
                  \end{equation}
                  Consequently,
                  \begin{equation}
                      \label{eq.inexact-inner-product-advanced}
                      \left\langle \nabla f(x+d),-d\right\rangle
                      \ge
                      c_{\rm in}
                      \frac{\|\nabla f(x+d)\|^{3/2}}{\sqrt M},
                  \end{equation}
                  where
                  \begin{equation}
                      \label{eq.cin-def}
                      c_{\rm in}
                      :=
                      \frac{4\eta^{1/4}}{6^{3/4}\sqrt{\beta}}
                      =
                      \frac{4}{6^{3/4}\sqrt{\beta}}
                      \left(\frac{1-(\frac12+\gamma_1)^2}{2}\right)^{1/4}.
                  \end{equation}
              \end{lemma}
              \begin{proof}
                  By Assumption~2.1,
                  \[
                      \left\|
                      \nabla f(x+d)-\nabla f(x)-\nabla^2 f(x)d
                      \right\|
                      \le
                      \frac{M}{2}\|d\|^2.
                  \]
                  Combining this with the inexact residual condition gives
                  \[
                      \|\nabla f(x+d)+\mu d\|
                      \le
                      \left(\frac12+\gamma_1\right)M\|d\|^2
                      =
                      \delta M\|d\|^2.
                  \]
                  Since \(\mu\ge M\|d\|\), we further have
                  \[
                      \|\nabla f(x+d)+\mu d\|
                      \le
                      \delta \mu\|d\|.
                  \]
                  Define
                  \[
                      w:=\nabla f(x+d)+\mu d.
                  \]
                  Then
                  \[
                      \nabla f(x+d)=-\mu d+w,
                      \qquad
                      \|w\|\le \delta\mu\|d\|.
                  \]
                  Therefore,
                  \[
                      \left\langle \nabla f(x+d),-d\right\rangle
                      =
                      \mu\|d\|^2-\langle w,d\rangle,
                  \]
                  and
                  \[
                      \|\nabla f(x+d)\|^2
                      =
                      \|-\mu d+w\|^2
                      =
                      \mu^2\|d\|^2-2\mu\langle w,d\rangle+\|w\|^2.
                  \]
                  Hence
                  \begin{align*}
                      \left\langle \nabla f(x+d),-d\right\rangle
                      -
                      \frac{\|\nabla f(x+d)\|^2}{2\mu}
                       & =
                      \mu\|d\|^2-\langle w,d\rangle
                      -
                      \frac{1}{2\mu}
                      \left(
                      \mu^2\|d\|^2-2\mu\langle w,d\rangle+\|w\|^2
                      \right)                                \\
                       & =
                      \frac12\mu\|d\|^2-\frac{\|w\|^2}{2\mu} \\
                       & \ge
                      \frac12\mu\|d\|^2
                      -
                      \frac{\delta^2\mu^2\|d\|^2}{2\mu}      \\
                       & =
                      \frac{1-\delta^2}{2}\mu\|d\|^2.
                  \end{align*}
                  This proves \eqref{eq.inexact-inner-product-first}.\\
                  Next, using \(\mu\le \beta M\|d\|\), we have
                  \[
                      \|d\|
                      \ge
                      \frac{\mu}{\beta M}.
                  \]
                  Therefore, from \eqref{eq.inexact-inner-product-first},
                  \[
                      \left\langle \nabla f(x+d),-d\right\rangle
                      \ge
                      \frac{\|\nabla f(x+d)\|^2}{2\mu}
                      +
                      \eta\mu\|d\|^2
                      \ge
                      \frac{\|\nabla f(x+d)\|^2}{2\mu}
                      +
                      \frac{\eta\mu^3}{\beta^2M^2}.
                  \]
                  Let \(p:=\|\nabla f(x+d)\|\). If \(p=0\), then
                  \eqref{eq.inexact-inner-product-advanced} holds trivially. If \(p>0\),
                  minimizing the right-hand side over \(\mu>0\) yields
                  \[
                      \frac{p^2}{2\mu}
                      +
                      \frac{\eta\mu^3}{\beta^2M^2}
                      \ge
                      \frac{4\eta^{1/4}}{6^{3/4}\sqrt{\beta}}
                      \frac{p^{3/2}}{\sqrt M}.
                  \]
                  This proves \eqref{eq.inexact-inner-product-advanced}.
              \end{proof}
              The same complexity can still be preserved by increasing only
              the constant in the estimating sequence. Specifically, define
              \[
                  C_{\rm in}
                  :=
                  \max\left\{
                  8,\frac{4}{3c_{\rm in}^2}
                  \right\},
              \]
              and replace the initial estimate sequence by
              \[
                  \phi_0(x)=C_{\rm in}M\|x-x_0\|^3,
              \]
              with the corresponding minimizer update
              \[
                  v_{k+1}
                  =
                  x_0-\sqrt{
                      \frac{1}{3C_{\rm in}M\|s_{k+1}\|}
                  }
                  s_{k+1}.
              \]
              The estimating-sequence proof then goes through with \(8M\) replaced by
              \(C_{\rm in}M\). Consequently,
              \[
                  f(x_k)-f^*
                  \le
                  \frac{C_{\rm in}M\|x^*-x_0\|^3}{A_k}
                  \le
                  \frac{6C_{\rm in}M\|x^*-x_0\|^3}{k^3}.
              \]
              Since \(C_{\rm in}\) depends only on the fixed inexactness parameters
              \(\gamma_1,\gamma_2\), and not on \(\epsilon_f\), the accelerated global
              complexity remains
              \(
              \tilde O(\epsilon_f^{-1/3}).
              \)\\
              \paragraph{Local detection} We first note that the local trigger \(\lambda_k=0\) is exact in the
              exact-oracle case, but under relative inexactness one should be slightly
              more careful. The inexact conditions imply an explicit upper bound on
              \(\lambda_k\), and \(\lambda_k=0\) follows once \(y_k\) enters a slightly
              smaller local region.\\
              Recall that
              \[
                  \sigma_k=\frac{\sqrt{2M}}{2}\|g_k\|^{1/2},
                  \qquad
                  r_k=\frac{\sqrt{2}}{2\sqrt M}\|g_k\|^{1/2}.
              \]
              Equivalently,
              \[
                  \sigma_k=Mr_k,
                  \qquad
                  \|g_k\|=2Mr_k^2=2\sigma_k r_k.
              \]
              \begin{lemma}
                  \label{lem.inexact-lambda-local-upper}
                  Suppose Assumptions~2.1 and 3.1 hold. Suppose \(y_k\in\mathcal{LQ}_g\) and \(\|g_k\|>0\). Let
                  \[
                      \sigma_k=\frac{\sqrt{2M}}{2}\|g_k\|^{1/2},
                      \qquad
                      r_k=\frac{\sqrt 2}{2\sqrt M}\|g_k\|^{1/2}.
                  \]
                  Equivalently,
                  \[
                      \sigma_k=Mr_k,
                      \qquad
                      \|g_k\|=2Mr_k^2.
                  \]
                  Assume that the inexact primal-dual pair \((d_k,\lambda_k)\) satisfies
                  \begin{align}
                      \label{eq.opt-inexact-fo-local}
                      \|g_k+(H_k+\sigma_k I+\lambda_k I)d_k\|
                       & \leq \gamma_1 M\|d_k\|^2, \\
                      \label{eq.opt-inexact-primal-local}
                      \|d_k\|
                       & \leq r_k,                 \\
                      \label{eq.opt-inexact-cs-local}
                      \gamma_2\lambda_k r_k
                       & \leq \lambda_k \|d_k\|,
                  \end{align}
                  where \(\gamma_1\in[0,1)\) and \(\gamma_2\in(0,1]\). Then
                  \begin{equation}
                      \label{eq.lambda-local-upper-simple}
                      0\le \lambda_k
                      \le
                      \left[
                          \left(
                          \gamma_1+\frac{2}{\gamma_2^2}-1
                          \right)\sigma_k
                          -
                          \frac{\nu}{3}
                          \right]_+,
                  \end{equation}
                  where \([a]_+:=\max\{a,0\}\). Consequently, if
                  \begin{equation}
                      \label{eq.inexact-smaller-lqg-simple}
                      \|\nabla f(y_k)\|
                      <
                      \frac{2\nu^2}{
                          9M
                          \left(
                          \gamma_1+\frac{2}{\gamma_2^2}-1
                          \right)^2
                      },
                  \end{equation}
                  then
                  \(
                  \lambda_k=0.
                  \)
              \end{lemma}
              \begin{proof}
                  Since \(y_k\in\mathcal{LQ}_g\), we have
                  \(
                  H_k\succeq \frac{\nu}{3}I.
                  \)
                  If \(\lambda_k=0\), then \eqref{eq.lambda-local-upper-simple} is immediate.
                  Hence we only consider the case \(\lambda_k>0\).\\
                  From the approximate complementarity condition
                  \eqref{eq.opt-inexact-cs-local}, since \(\lambda_k>0\), we obtain
                  \[
                      \gamma_2 r_k\le \|d_k\|.
                  \]
                  Together with \eqref{eq.opt-inexact-primal-local}, this gives
                  \begin{equation}
                      \label{eq.local-d-range-simple}
                      \gamma_2 r_k\le \|d_k\|\le r_k.
                  \end{equation}
                  Define the residual
                  \[
                      e_k:=g_k+(H_k+\sigma_k I+\lambda_k I)d_k.
                  \]
                  Then by \eqref{eq.opt-inexact-fo-local},
                  \[
                      \|e_k\|\le \gamma_1M\|d_k\|^2.
                  \]
                  Moreover,
                  \[
                      (H_k+\sigma_k I+\lambda_k I)d_k=e_k-g_k.
                  \]
                  Since
                  \[
                      H_k+\sigma_k I+\lambda_k I
                      \succeq
                      \left(
                      \frac{\nu}{3}+\sigma_k+\lambda_k
                      \right)I,
                  \]
                  we have
                  \begin{align*}
                      \left(
                      \frac{\nu}{3}+\sigma_k+\lambda_k
                      \right)\|d_k\|
                       & \le
                      \|(H_k+\sigma_k I+\lambda_k I)d_k\| \\
                       & =
                      \|e_k-g_k\|                         \\
                       & \le
                      \|e_k\|+\|g_k\|                     \\
                       & \le
                      \gamma_1M\|d_k\|^2+\|g_k\|.
                  \end{align*}
                  Now, using \(\|d_k\|\ge \gamma_2 r_k\) and \(\|g_k\|=2Mr_k^2\), we directly bound
                  \[
                      \|g_k\|
                      =
                      2Mr_k^2
                      \le
                      \frac{2M}{\gamma_2^2}\|d_k\|^2.
                  \]
                  Therefore,
                  \[
                      \left(
                      \frac{\nu}{3}+\sigma_k+\lambda_k
                      \right)\|d_k\|
                      \le
                      \left(
                      \gamma_1+\frac{2}{\gamma_2^2}
                      \right)M\|d_k\|^2.
                  \]
                  Since \(\lambda_k>0\) implies \(\|d_k\|\ge \gamma_2 r_k>0\), we can divide both sides by \(\|d_k\|\) and obtain
                  \[
                      \frac{\nu}{3}+\sigma_k+\lambda_k
                      \le
                      \left(
                      \gamma_1+\frac{2}{\gamma_2^2}
                      \right)M\|d_k\|.
                  \]
                  Using \(\|d_k\|\le r_k\) and \(\sigma_k=Mr_k\), we get
                  \begin{align*}
                      \lambda_k
                       & \le
                      \left(
                      \gamma_1+\frac{2}{\gamma_2^2}
                      \right)Mr_k
                      -\sigma_k
                      -\frac{\nu}{3} \\
                       & =
                      \left(
                      \gamma_1+\frac{2}{\gamma_2^2}-1
                      \right)\sigma_k
                      -\frac{\nu}{3}.
                  \end{align*}
                  Together with \(\lambda_k\ge0\), this proves
                  \[
                      0\le \lambda_k
                      \le
                      \left[
                          \left(
                          \gamma_1+\frac{2}{\gamma_2^2}-1
                          \right)\sigma_k
                          -
                          \frac{\nu}{3}
                          \right]_+.
                  \]
                  It remains to prove the sufficient condition for \(\lambda_k=0\). Since
                  \[
                      \sigma_k=\frac{\sqrt{2M}}{2}\|\nabla f(y_k)\|^{1/2}
                      =
                      \sqrt{\frac{M\|\nabla f(y_k)\|}{2}},
                  \]
                  condition \eqref{eq.inexact-smaller-lqg-simple} implies
                  \[
                      \sigma_k
                      <
                      \frac{\nu}{
                          3\left(
                          \gamma_1+\frac{2}{\gamma_2^2}-1
                          \right)
                      }.
                  \]
                  Hence
                  \[
                      \left(
                      \gamma_1+\frac{2}{\gamma_2^2}-1
                      \right)\sigma_k
                      -
                      \frac{\nu}{3}
                      <0.
                  \]
                  Therefore, by \eqref{eq.lambda-local-upper-simple}, we must have
                  \(
                  \lambda_k=0.
                  \)
              \end{proof}
              The above results implies the detection mechanism $\lambda_k$ detects a smaller local region in the case that the subproblems are solved inexactly. We can detects the region $\mathcal{LQ}_g$ by \eqref{eq.lambda-local-upper-simple}.
          }

    \item \comm{The current ratio conditions and numerical experiments rely on a conservative global estimate of the Lipschitz constant $M$. While theoretically sufficient, this limits practical efficiency. The authors should discuss whether an adaptive backtracking strategy for $M_k$ could be integrated into the $\trp$ framework without degrading the $\widetilde{O}(\epsilon^{-1/3})$ complexity.}

          {
              \color{blue}
              Response: Thank you for the question. A monotone adaptive backtracking strategy can be incorporated into the \(\trp\) framework without degrading the global \(\widetilde O(\epsilon^{-1/3})\) oracle complexity, the analysis is similar to \cite{jiang2020unified,he2025history}. The key idea is to replace the algorithmic dependence on the exact value of \(M\) in Lemma~2.3 by a verifiable backtracking certificate. Throughout this response, \(M\) denotes the true Hessian Lipschitz constant in Assumption~2.1, while \(M_k\) denotes the adaptive estimate maintained by the algorithm. The trial estimate used inside the \(k\)-th iteration is denoted by \(\widehat M_k\). The resulting scheme is summarized below.
              \begin{algorithm}[htbp]
                  \caption{Accelerated TR with Backtracking}\label{alg.accelerated-utr-backtrack}
                  \begin{algorithmic}[1]
                      \STATE \textbf{Input:} initial point \(x_0=v_0\in \mathbb{R}^n\), \(s_0=0\), initial estimate \(M_0>0\), backtracking factor \(\gamma_b>1\), \(n_f=0\).
                      \FOR{\(k=0,1,2,\ldots\)}
                      \STATE \(\widehat M_k\leftarrow M_k\), \(\operatorname{accept}\leftarrow \mathrm{False}\).
                      \WHILE{\(\operatorname{accept}=\mathrm{False}\)}
                      \IF{\(s_k=0\)}
                      \STATE \(\widehat v_k=x_0\).
                      \ELSE
                      \STATE \(\displaystyle \widehat v_k=x_0-\sqrt{\frac{1}{24\widehat M_k\|s_k\|}}s_k\).
                      \ENDIF
                      \STATE \(\displaystyle y_k=\frac{k}{k+3}x_k+\frac{3}{k+3}\widehat v_k\).
                      \STATE \(\displaystyle
                      (\sigma_k,r_k)
                      =
                      \left(
                      \frac{\sqrt{2\widehat M_k}}{2}\|\nabla f(y_k)\|^{1/2},
                      \frac{1}{\sqrt{2\widehat M_k}}\|\nabla f(y_k)\|^{1/2}
                      \right).
                      \)
                      \label{line.adaptive-set-params}
                      \STATE \((d_k,\lambda_k)=\trp(y_k,\sigma_k,r_k)\), and set \(\mu_k=\sigma_k+\lambda_k\).
                      \IF{\(\lambda_k=0\)}
                      \STATE Use R\&B at \(y_k\) with ratio target \(\widehat M_k\) to replace \((d_k,\mu_k)\) so that
                      \[
                          (\nabla^2 f(y_k)+\mu_k I)d_k=-\nabla f(y_k),
                          \qquad
                          \widehat M_k\|d_k\|\le \mu_k\le 2\widehat M_k\|d_k\|.
                      \]
                      \ENDIF
                      \IF{
                          \(\displaystyle
                          \left\langle \nabla f(y_k+d_k),-d_k\right\rangle
                          <
                          \frac{\sqrt 6}{6}
                          \frac{\|\nabla f(y_k+d_k)\|^{3/2}}{\sqrt{\widehat M_k}}
                          \)
                      }
                      \label{line.adaptive-backtrack-test}
                      \STATE \(\widehat M_k\leftarrow \gamma_b\widehat M_k\).
                      \STATE \(n_f\leftarrow n_f+1\).
                      \ELSE
                      \STATE \(\operatorname{accept}\leftarrow \mathrm{True}\).
                      \ENDIF
                      \ENDWHILE
                      \STATE \(M_{k+1}=\widehat M_k\).
                      \STATE \(x_{k+1}=y_k+d_k\).
                      \STATE \(\displaystyle s_{k+1}=s_k+\frac{(k+1)(k+2)}{2}\nabla f(x_{k+1})\).
                      \label{line.adaptive-update-s}
                      \STATE \(\displaystyle v_{k+1}
                      = x_0-\sqrt{\frac{1}{24M_{k+1}\|s_{k+1}\|}}s_{k+1}\).
                      \label{line.adaptive-update-v}
                      \ENDFOR
                  \end{algorithmic}
              \end{algorithm}

              The main difference from Algorithm 1 is that whenever the trial estimate \(\widehat M_k\) is increased, we recompute not only the parameters \((\sigma_k,r_k)\), but also the current estimate-sequence minimizer \(\widehat v_k\) and the extrapolation point \(y_k\). This is necessary because the cubic coefficient in the estimate sequence depends on the current value of the adaptive estimate.

              More precisely, let
              \[
                  a_k=\frac{(k+1)(k+2)}{2},
                  \qquad
                  A_k=\frac{k(k+1)(k+2)}{6},
                  \qquad
                  A_{k+1}=A_k+a_k.
              \]
              The adaptive estimating sequence is defined as
              \begin{equation}
                  \label{eq.adaptive-phi0}
                  \phi_0(x)=8M_0\|x-x_0\|^3,
              \end{equation}
              and
              \begin{equation}
                  \label{eq.adaptive-phi-update}
                  \begin{aligned}
                      \phi_{k+1}(x)
                       & =
                      \phi_k(x)
                      +
                      8(M_{k+1}-M_k)\|x-x_0\|^3 \\
                       & \quad
                      +
                      a_k
                      \left(
                      f(x_{k+1})
                      +
                      \left\langle \nabla f(x_{k+1}),x-x_{k+1}\right\rangle
                      \right).
                  \end{aligned}
              \end{equation}
              Equivalently, during the backtracking loop, if the trial value is \(\widehat M_k\), we temporarily use
              \begin{equation}
                  \label{eq.adaptive-temp-phi}
                  \widehat \phi_k(x)
                  =
                  \phi_k(x)
                  +
                  8(\widehat M_k-M_k)\|x-x_0\|^3.
              \end{equation}
              Then \(\widehat v_k\) in \Cref{alg.accelerated-utr-backtrack} is exactly
              \[
                  \widehat v_k=\arg\min_{x\in\mathbb R^n}\widehat \phi_k(x),
              \]
              and the accepted update \eqref{eq.adaptive-phi-update} is equivalent to
              \[
                  \phi_{k+1}(x)
                  =
                  \widehat \phi_k(x)
                  +
                  a_k
                  \left(
                  f(x_{k+1})
                  +
                  \left\langle \nabla f(x_{k+1}),x-x_{k+1}\right\rangle
                  \right).
              \]

              We first show that the backtracking procedure terminates after a uniformly bounded number of failed trials.

              \begin{lemma}
                  \label{lem.adaptive-finite-backtracking}
                  Suppose Assumption~2.1 holds. Let \(\widehat M>0\) be a trial estimate, and suppose that the step \(d\) and the regularization parameter \(\mu\) satisfy
                  \begin{equation}
                      \label{eq.adaptive-ratio}
                      (\nabla^2 f(y)+\mu I)d=-\nabla f(y),
                      \qquad
                      \widehat M\|d\|\le \mu\le 2\widehat M\|d\|.
                  \end{equation}
                  If \(\widehat M\ge M\), then
                  \begin{equation}
                      \label{eq.adaptive-bt-pass}
                      \left\langle \nabla f(y+d),-d\right\rangle
                      \ge
                      \frac{\sqrt 6}{6}
                      \frac{\|\nabla f(y+d)\|^{3/2}}{\sqrt{\widehat M}}.
                  \end{equation}
                  Consequently, the total number \(n_f\) of failed backtracking trials in \Cref{alg.accelerated-utr-backtrack} satisfies
                  \begin{equation}
                      \label{eq.nf-bound}
                      n_f
                      \le
                      \left\lceil
                      \log_{\gamma_b}\frac{M}{M_0}
                      \right\rceil_+,
                      \qquad
                      \left\lceil t\right\rceil_+:=\max\{\lceil t\rceil,0\}.
                  \end{equation}
                  Moreover,
                  \begin{equation}
                      \label{eq.Mk-upper}
                      M_k\le M_{\max}:=\max\{M_0,\gamma_b M\},
                      \qquad
                      \forall k\ge0.
                  \end{equation}
              \end{lemma}

              \begin{proof}
                  Since \(\widehat M\ge M\) and \(\mu\ge \widehat M\|d\|\), we have
                  \[
                      \mu\ge M\|d\|.
                  \]
                  Therefore, by Lemma 2.3,
                  \begin{equation}
                      \label{eq.bt-proof-1}
                      \left\langle \nabla f(y+d),-d\right\rangle
                      \ge
                      \frac{\|\nabla f(y+d)\|^2}{2\mu}
                      +
                      \frac{3}{8}\mu\|d\|^2.
                  \end{equation}
                  Let
                  \[
                      \nabla f(x+d):=\nabla f(y+d),
                      \qquad
                      p:=\|\nabla f(x+d)\|.
                  \]
                  From \(\mu\le 2\widehat M\|d\|\), we obtain
                  \[
                      \|d\|\ge \frac{\mu}{2\widehat M}.
                  \]
                  Substituting this into \eqref{eq.bt-proof-1} gives
                  \[
                      \left\langle \nabla f(x+d),-d\right\rangle
                      \ge
                      \frac{p^2}{2\mu}
                      +
                      \frac{3}{8}\mu\cdot \frac{\mu^2}{4\widehat M^2}
                      =
                      \frac{p^2}{2\mu}
                      +
                      \frac{3\mu^3}{32\widehat M^2}.
                  \]
                  If \(p=0\), then \eqref{eq.adaptive-bt-pass} is immediate. If \(p>0\), minimizing the right-hand side over \(\mu>0\) yields
                  \[
                      \frac{p^2}{2\mu}
                      +
                      \frac{3\mu^3}{32\widehat M^2}
                      \ge
                      \frac{1}{\sqrt 3}
                      \frac{p^{3/2}}{\sqrt{\widehat M}}.
                  \]
                  Since
                  \[
                      \frac{1}{\sqrt 3}
                      >
                      \frac{\sqrt 6}{6},
                  \]
                  we obtain
                  \[
                      \left\langle \nabla f(y+d),-d\right\rangle
                      \ge
                      \frac{\sqrt 6}{6}
                      \frac{\|\nabla f(y+d)\|^{3/2}}{\sqrt{\widehat M}}.
                  \]
                  Thus the backtracking test must pass whenever the trial estimate satisfies \(\widehat M\ge M\).

                  Since the trial estimate is multiplied by \(\gamma_b>1\) after each failed trial, the number of failed trials before reaching a value no smaller than \(M\) is at most
                  \[
                      \left\lceil
                      \log_{\gamma_b}\frac{M}{M_0}
                      \right\rceil_+.
                  \]
                  This proves \eqref{eq.nf-bound}. The bound \eqref{eq.Mk-upper} follows because the first accepted trial value after crossing \(M\) can overshoot \(M\) by at most a factor \(\gamma_b\).
              \end{proof}

              Next we show that the estimate-sequence argument is preserved under this adaptive update.

              \begin{lemma}
                  \label{lem.adaptive-estimate-sequence}
                  Suppose \(f\) is convex and Assumption~2.1 holds. Let \(\{\phi_k\}_{k\ge0}\) be defined by \eqref{eq.adaptive-phi0} and \eqref{eq.adaptive-phi-update}. Suppose that every accepted step in \Cref{alg.accelerated-utr-backtrack} satisfies
                  \begin{equation}
                      \label{eq.accepted-bt-condition}
                      \left\langle \nabla f(x_{k+1}),y_k-x_{k+1}\right\rangle
                      \ge
                      \frac{\sqrt 6}{6}
                      \frac{\|\nabla f(x_{k+1})\|^{3/2}}{\sqrt{M_{k+1}}}.
                  \end{equation}
                  Then, for all \(k\ge0\),
                  \begin{equation}
                      \label{eq.adaptive-estimating-sequence-relation}
                      A_k f(x_k)
                      \le
                      \phi_k^*
                      \le
                      \phi_k(x)
                      \le
                      A_k f(x)+8M_k\|x-x_0\|^3,
                      \qquad
                      \forall x\in\mathbb R^n.
                  \end{equation}
                  In particular, since \(M_k=\gamma_b^{n_f(k)}M_0\), where \(n_f(k)\) is the number of failed backtracking trials before the beginning of iteration \(k\), we also have
                  \begin{equation}
                      \label{eq.adaptive-estimating-sequence-relation-nf}
                      \phi_k(x)
                      \le
                      A_k f(x)+8\gamma_b^{n_f(k)}M_0\|x-x_0\|^3,
                      \qquad
                      \forall x\in\mathbb R^n.
                  \end{equation}
              \end{lemma}

              \begin{proof}
                  We prove \eqref{eq.adaptive-estimating-sequence-relation} by induction.

                  For \(k=0\), we have \(A_0=0\) and
                  \[
                      \phi_0(x)=8M_0\|x-x_0\|^3.
                  \]
                  Hence \(\phi_0^*=0=A_0f(x_0)\), and \eqref{eq.adaptive-estimating-sequence-relation} holds.

                  Suppose that \eqref{eq.adaptive-estimating-sequence-relation} holds for some \(k\ge0\). Let \(M_{k+1}\) be the accepted estimate in the \(k\)-th iteration, and define
                  \[
                      \widehat \phi_k(x)
                      =
                      \phi_k(x)+8(M_{k+1}-M_k)\|x-x_0\|^3.
                  \]
                  By the induction hypothesis,
                  \begin{equation}
                      \label{eq.adaptive-upper-hatphi}
                      \widehat \phi_k(x)
                      \le
                      A_k f(x)+8M_{k+1}\|x-x_0\|^3,
                      \qquad
                      \forall x\in\mathbb R^n.
                  \end{equation}
                  Moreover, since \(M_{k+1}\ge M_k\),
                  \begin{equation}
                      \label{eq.adaptive-hatphi-star}
                      \widehat \phi_k^*
                      =
                      \min_x \widehat \phi_k(x)
                      \ge
                      \min_x \phi_k(x)
                      =
                      \phi_k^*
                      \ge
                      A_k f(x_k).
                  \end{equation}

                  We first verify the upper estimate-sequence relation. By \eqref{eq.adaptive-phi-update},
                  \[
                      \phi_{k+1}(x)
                      =
                      \widehat \phi_k(x)
                      +
                      a_k
                      \left(
                      f(x_{k+1})
                      +
                      \left\langle \nabla f(x_{k+1}),x-x_{k+1}\right\rangle
                      \right).
                  \]
                  Combining this with \eqref{eq.adaptive-upper-hatphi} and the convexity of \(f\), we have
                  \begin{align*}
                      \phi_{k+1}(x)
                       & \le
                      A_k f(x)+8M_{k+1}\|x-x_0\|^3          \\
                       & \quad
                      +
                      a_k
                      \left(
                      f(x_{k+1})
                      +
                      \left\langle \nabla f(x_{k+1}),x-x_{k+1}\right\rangle
                      \right)                               \\
                       & \le
                      A_k f(x)+8M_{k+1}\|x-x_0\|^3+a_k f(x) \\
                       & =
                      A_{k+1}f(x)+8M_{k+1}\|x-x_0\|^3.
                  \end{align*}
                  Thus the rightmost inequality in \eqref{eq.adaptive-estimating-sequence-relation} holds for \(k+1\).

                  We now prove the lower estimate-sequence relation. Since \(\widehat \phi_k\) has the form
                  \[
                      \widehat \phi_k(x)
                      =
                      c_k+\langle s_k,x\rangle+8M_{k+1}\|x-x_0\|^3
                  \]
                  for some scalar \(c_k\), its minimizer is exactly
                  \[
                      \widehat v_k
                      =
                      \arg\min_x \widehat \phi_k(x)
                      =
                      x_0-\sqrt{\frac{1}{24M_{k+1}\|s_k\|}}s_k
                  \]
                  with the convention \(\widehat v_k=x_0\) if \(s_k=0\). Moreover, using the same cubic growth property as in equation~(A.3), we have
                  \begin{equation}
                      \label{eq.adaptive-cubic-growth}
                      \widehat \phi_k(x)
                      \ge
                      \widehat \phi_k^*
                      +
                      4M_{k+1}\|x-\widehat v_k\|^3,
                      \qquad
                      \forall x\in\mathbb R^n.
                  \end{equation}
                  Combining \eqref{eq.adaptive-hatphi-star} and \eqref{eq.adaptive-cubic-growth}, we obtain
                  \begin{equation}
                      \label{eq.adaptive-lower-hatphi}
                      \widehat \phi_k(x)
                      \ge
                      A_k f(x_k)+4M_{k+1}\|x-\widehat v_k\|^3.
                  \end{equation}

                  Let
                  \[
                      g_{k+1}:=\nabla f(x_{k+1}).
                  \]
                  Then
                  \begin{align*}
                      \phi_{k+1}^*
                       & =
                      \min_{x\in\mathbb R^n}
                      \left\{
                      \widehat \phi_k(x)
                      +
                      a_k
                      \left(
                      f(x_{k+1})
                      +
                      \langle g_{k+1},x-x_{k+1}\rangle
                      \right)
                      \right\}                     \\
                       & \ge
                      \min_{x\in\mathbb R^n}
                      \Bigl\{
                      A_k f(x_k)
                      +
                      4M_{k+1}\|x-\widehat v_k\|^3 \\
                       & \qquad\qquad\qquad
                      +
                      a_k
                      \left(
                      f(x_{k+1})
                      +
                      \langle g_{k+1},x-x_{k+1}\rangle
                      \right)
                      \Bigr\}.
                  \end{align*}
                  By convexity of \(f\),
                  \[
                      f(x_k)
                      \ge
                      f(x_{k+1})+\langle g_{k+1},x_k-x_{k+1}\rangle.
                  \]
                  Therefore,
                  \begin{align*}
                      \phi_{k+1}^*
                       & \ge
                      \min_{x\in\mathbb R^n}
                      \Bigl\{
                      A_k f(x_{k+1})
                      +
                      A_k\langle g_{k+1},x_k-x_{k+1}\rangle \\
                       & \qquad
                      +
                      4M_{k+1}\|x-\widehat v_k\|^3          \\
                       & \qquad
                      +
                      a_k f(x_{k+1})
                      +
                      a_k\langle g_{k+1},x-x_{k+1}\rangle
                      \Bigr\}                               \\
                       & =
                      A_{k+1}f(x_{k+1})
                      +
                      \left\langle g_{k+1},
                      A_kx_k+a_k\widehat v_k-A_{k+1}x_{k+1}
                      \right\rangle                         \\
                       & \qquad
                      +
                      \min_{z\in\mathbb R^n}
                      \left\{
                      4M_{k+1}\|z\|^3
                      +
                      a_k\langle g_{k+1},z\rangle
                      \right\},
                  \end{align*}
                  where \(z=x-\widehat v_k\). The last minimum is
                  \[
                      \min_{z\in\mathbb R^n}
                      \left\{
                      4M_{k+1}\|z\|^3
                      +
                      a_k\langle g_{k+1},z\rangle
                      \right\}
                      =
                      -
                      \frac{a_k^{3/2}}{3\sqrt{3M_{k+1}}}
                      \|g_{k+1}\|^{3/2}.
                  \]
                  Hence
                  \begin{align*}
                      \phi_{k+1}^*
                       & \ge
                      A_{k+1}f(x_{k+1})
                      +
                      A_{k+1}
                      \left\langle
                      g_{k+1},
                      \frac{A_k}{A_{k+1}}x_k
                      +
                      \frac{a_k}{A_{k+1}}\widehat v_k
                      -
                      x_{k+1}
                      \right\rangle \\
                       & \qquad
                      -
                      \frac{a_k^{3/2}}{3\sqrt{3M_{k+1}}}
                      \|g_{k+1}\|^{3/2}.
                  \end{align*}
                  By the definition of \(y_k\) in \Cref{alg.accelerated-utr-backtrack},
                  \[
                      y_k
                      =
                      \frac{A_k}{A_{k+1}}x_k
                      +
                      \frac{a_k}{A_{k+1}}\widehat v_k.
                  \]
                  Thus
                  \begin{align*}
                      \phi_{k+1}^*
                       & \ge
                      A_{k+1}f(x_{k+1})
                      +
                      A_{k+1}
                      \left(
                      \langle g_{k+1},y_k-x_{k+1}\rangle
                      -
                      \frac{a_k^{3/2}}{3\sqrt{3}A_{k+1}}
                      \frac{\|g_{k+1}\|^{3/2}}{\sqrt{M_{k+1}}}
                      \right).
                  \end{align*}
                  Using
                  \[
                      \frac{a_k^{3/2}}{3\sqrt{3}A_{k+1}}
                      =
                      \frac{\sqrt{(k+1)(k+2)}}{\sqrt 6(k+3)}
                      \le
                      \frac{1}{\sqrt 6}
                      =
                      \frac{\sqrt 6}{6},
                  \]
                  we get
                  \begin{align*}
                      \phi_{k+1}^*
                       & \ge
                      A_{k+1}f(x_{k+1})
                      +
                      A_{k+1}
                      \left(
                      \langle g_{k+1},y_k-x_{k+1}\rangle
                      -
                      \frac{\sqrt 6}{6}
                      \frac{\|g_{k+1}\|^{3/2}}{\sqrt{M_{k+1}}}
                      \right).
                  \end{align*}
                  Finally, by the accepted backtracking condition \eqref{eq.accepted-bt-condition}, the term in parentheses is nonnegative. Therefore,
                  \[
                      \phi_{k+1}^*
                      \ge
                      A_{k+1}f(x_{k+1}).
                  \]
                  This completes the induction proof of \eqref{eq.adaptive-estimating-sequence-relation}. The bound \eqref{eq.adaptive-estimating-sequence-relation-nf} follows from the identity \(M_k=\gamma_b^{n_f(k)}M_0\).
              \end{proof}

              We now explain why the complexity is unchanged. Taking \(x=x^*\) in \eqref{eq.adaptive-estimating-sequence-relation}, we obtain
              \[
                  A_k f(x_k)
                  \le
                  \phi_k^*
                  \le
                  \phi_k(x^*)
                  \le
                  A_k f^*
                  +
                  8M_k\|x^*-x_0\|^3.
              \]
              Therefore,
              \[
                  f(x_k)-f^*
                  \le
                  \frac{8M_k\|x^*-x_0\|^3}{A_k}.
              \]
              By \Cref{lem.adaptive-finite-backtracking}, \(M_k\le M_{\max}:=\max\{M_0,\gamma_b M\}\). Hence
              \[
                  f(x_k)-f^*
                  \le
                  \frac{8M_{\max}\|x^*-x_0\|^3}{A_k}\leq \frac{8M_{\max}\|x^*-x_0\|^3}{k^3}.
              \]
              Thus an \(\epsilon_f\)-function-value solution is obtained after
              \[
                  k
                  =
                  O\left(
                  \left(
                      \frac{M_{\max}\|x^*-x_0\|^3}{\epsilon_f}
                      \right)^{1/3}
                  \right)
                  =
                  O(\epsilon_f^{-1/3})
              \]
              iterations.
          }
\end{itemize}

\subsection{Typos}

\begin{itemize}
    \item \comm{Page 4, line 43: There is an extra space before the period in ``can be designed .''.}

          \resp{Thank you. We have removed the extra space.}

    \item \comm{Page 4, line 50: The phrase ``hold, holds'' appears to be a typo. Moreover, the expression ``for some $\mu \ge M\|d\|$'' seems to modify both Assumption 2.1 and (2.5), while Assumption 2.1 is independent of $\mu$. It may be clearer to write: ``Suppose that Assumption 2.1 holds and that (2.5) holds for some $\mu \ge M\|d\|$.''}

          \resp{Thank you. We have revised the sentence as suggested.}

    \item \comm{Page 8, line 29: $\sqrt{\frac{1}{2M}}\|\nabla f(y_k)\|$ should be $\sqrt{\frac{1}{2M}}\|\nabla f(y_k)\|^{1/2}$.}

          \resp{Thank you. We have corrected this expression.}

    \item \comm{Page 8, line 31: $\sqrt{2M\|\nabla f(y_k)\|}$ should be $\sqrt{2M}\|\nabla f(y_k)\|^{1/2}$.}

          \resp{Thank you. We have corrected this expression.}

    \item \comm{Page 12, lines 19--21: $\nabla f$ should be $\nabla^2 f$. There is also a missing period in equation (3.22).}

          \resp{Thank you. We have corrected the notation and added the missing period.}

    \item \comm{Page 20, line 22: $-\frac{M}{4}\|d\|^4$ should be $-\frac{M^2}{4}\|d\|^4$.}

          \resp{Thank you. We have corrected this typo.}
\end{itemize}
