\section{Response to Reviewer 1}
\resp{We sincerely thank you for your careful reading of our manuscript and for your detailed, constructive, and insightful comments. We have revised the manuscript accordingly and have answered all your questions in detail. In particular, we have improved the organization and notation, clarified the algorithmic descriptions, added missing proof details, corrected the typos and derivation issues you pointed out, and provided additional explanations for the numerical experiments. We are grateful for your suggestions, which helped us substantially improve the clarity, rigor, and presentation of the paper.}
\subsection{Major concerns}

\paragraph{General organization of the paper}
\begin{itemize}
      \item \comm{Definition 2.1 can be introduced earlier, as the authors refer to that in the introduction, for example on Page 1, line 55.}

            \resp{Thank you for pointing this out. We have revised the introduction to avoid referring to Definition~2.1 before it is introduced.}

      \item \comm{Assumption 2.3: the authors can comment that this is equivalent to Lipschitz gradient.}

            \resp{Thank you. We have added this comment.}

      \item \comm{Notation: please include more details about the notation used in the Preliminaries section, on Page 4, line 4. For example, the authors denote by $x_k$, $v_k$, and $s_k$ the iterates of Algorithm 1. These quantities are used in the lemmas, for example Lemma 2.3, and it is not obvious whether they refer to the iterates from the algorithm or to general vectors.}

            \resp{Thank you. We have added the suggested details to clarify that $x_k$, $v_k$, and $s_k$ refer to the iterates generated by Algorithm~1.}

      \item \comm{The authors sometimes use the same letter for different notation across the paper. I suggest avoiding this. For example, $\lambda_k$ is used as the dual variable for the constraint $\|d_k\| \le r_k$ in TR+, while in Lemma 3.6 the notation $\operatorname{diag}(\lambda_1,\ldots,\lambda_n)$ is used to represent eigenvalues.}

            \resp{Thank you. We have reviewed the notation throughout the paper and revised it to ensure consistency.}

      \item \comm{Please add text indicating that the proof of Lemma 4.4 appears in Appendix C.}

            \resp{Thank you. We have added the corresponding text.}

      \item \comm{Please add text indicating that the proof of Lemma 4.7 appears in Appendix C.}

            \resp{Thank you. We have added the corresponding text.}
\end{itemize}

\paragraph{Proofs and mathematical derivations}

\comm{In all proofs, the authors are encouraged to provide more detailed explanations of the transitions from one step to another, even if some of those transitions are trivial.}

\resp{Thank you for your detailed comments. We carefully reviewed all of our proofs and revised the manuscript accordingly. {\bf To improve the flow, the analysis for each variant is now organized into iteration complexity, oracle calls, and finally, oracle complexity.} We add more details to the derivations for the proofs to improve the clarity. For comments where the corresponding revisions are straightforward and self-explanatory, we have omitted detailed responses for brevity. Regarding your comment on Lemma 3.13, we have completely rewritten the result (now Lemma 3.11) and improved its dependence on $\nu$.}
\begin{itemize}
      \item \comm{Page 7, line 16. Even if it is obvious, mention when introducing the sequence $\{\phi_k(x)\}_{k\ge 0}$ that it is a monotone non-increasing sequence, since this property is used in Lemma 3.4.}

            \resp{Thanks for the comment. We do not use, nor claim, that $\phi_k(x)$ is non-increasing; this is generally false. The proof only relies on the way we define the estimating sequence.}

      \item \comm{Page 7, line 20. There is an issue because $A_0=0$. It would be better to comment on the provided inequality since it involves $1/A_k$.}

      \item \comm{Lemma 3.3, Page 8, line 25. There is a typo: $\mu_k=\sigma_k+r_k$ should be $\mu_k=\sigma_k+\lambda_k$. It would also be better to add that this follows by our choice of $(\sigma_k,r_k)$ in Algorithm 1, line 4.}

      \item \comm{Lemma 3.3, Page 8, line 29. There is a typo: $r_k=\sqrt{\frac{1}{2M}\|\nabla f(y_k)\|}$ should be $r_k=\sqrt{\frac{1}{2M}}\|\nabla f(y_k)\|^{1/2}$, based on Algorithm 1, line 4.}

      \item \comm{Lemma 3.3, Page 8, line 32. There is a typo due to the previous one. It should be
                  $\mu_k \le \frac{\|\nabla f(y_k)\|}{\|d_k\|}
                        = \sqrt{2M}\|\nabla f(y_k)\|^{1/2}
                        = 2M\|d_k\|$
                  instead of
                  $\mu_k \le \frac{\|\nabla f(y_k)\|}{\|d_k\|}
                        = \sqrt{2M}\|\nabla f(y_k)\|
                        = 2M\|d_k\|$.}

      \item \comm{Lemma 3.4, Page 8, line 45. Even if it is obvious, mention that the first equality follows from equation (3.3).}

      \item \comm{Lemma 3.4, Page 8, line 48. Please mention that the second inequality holds by the convexity of $f$.}

      \item \comm{Lemma 3.4, Page 8, line 49. Even if it is obvious, mention that the equality follows from the definitions of $A_k$ and $a_k$ in (3.2).}

      \item \comm{Lemma 3.4, Page 8, line 54. Please mention that this inequality follows from Lemma 3.2, and more precisely from equation (3.6).}

      \item \comm{Lemma 3.4, Page 8, line 7. Please provide more details about this equality. The manuscript says that ``the fifth line is from rearranging terms and solving the trivial minimization problem,'' but it would be better to provide more details, for example in the appendix.}

            \resp{We have added all the details in this proof.}

      \item \comm{Lemma 3.4, Page 8, line 10. Please mention that this follows from the definitions of $a_k$ and $A_k$ in (3.2).}

      \item \comm{Lemma 3.4, Page 8, line 24. Please mention that this uses Lemma 3.3.}

      \item \comm{Lemma 3.4, Page 8, line 22. There is a typo: it should be $\nabla f(x_{k+1}), y_k-x_{k+1}$ instead of $f(x_{k+1}), y_k-x_{k+1}$. The same issue appears on line 29.}

      \item \comm{Theorem 3.1. Please provide a proof, even if it is trivial and follows from the established inequalities and a telescoping-sum argument.}

      \item \comm{Lemma 3.5, Page 9, line 48. Please mention that using the Algorithm 1 update rule in line 4 for $\sigma_k$ and $r_k$, we have
                  $\sigma_k=\frac{\sqrt{2M}}{2}\|\nabla f(y_k)\|^{1/2}$
                  and
                  $r_k=\sqrt{\frac{1}{2M}}\|\nabla f(y_k)\|^{1/2}$,
                  hence the following results hold.}

      \item \comm{Corollary 3.1. For the first inequality, please mention that we use $\mu=\sigma$ since $\lambda=0$, together with
                  $\sigma=\frac{\sqrt{2M}}{2}\|\nabla f(y_k)\|^{1/2}$
                  from Algorithm 1.}

      \item \comm{From the statement of Lemma 3.5, by combining the bound on $\|d_+\|$ and the bound from $\|\nabla f(y_k)\|$, we obtain $\|d_+\|\le \kappa_H/M$. Does this affect any of the results for $k\in\mathcal{L}$?}

            \resp{Thanks for the detailed observation. No, it doesn't contradict with any results.}

      \item \comm{Page 10, line 56. It would be recommended to link this inequality to the results of Lemma 3.3, since this section is trying to establish the same result for the output of the R\&B Subroutine 1, i.e., for all $k\in\mathcal{L}$, similar to what has been established for all $k\in\mathcal{N}$ in Lemma 3.3.}

      \item \comm{Lemma 3.11. The proof uses $\|x-x^\ast\|\le r$, but no value of $r$ is specified. A quick comment can be added that Lemma 3.12 specifies the value of $r$.}

      \item \comm{Lemma 3.14, Page 13, line 25. Please add a minor detail referring to Algorithm 1, line 4, for the value of $\sigma_k$.}

      \item \comm{Lemma 3.14, Page 13, line 29. It would be recommended to add a reference to Algorithm 1, line 4, for the value of $r_k$.}

      \item \comm{Theorem 3.3, Page 13, line 51. Please add a reference to Corollary 3.1 when proving the first case for line 3 of Subroutine 1.}

      \item \comm{Lemma 4.1, Page 15, line 32. Typo: it should refer to Lemma 2.1 instead of Assumption 2.1.}

      \item \comm{Lemma 4.1, Page 15, line 42. For the last inequality, please add more details about the derivation. For example, mention that $\|d_-\|\le r_-$, where $r_-=\frac{1}{M}\sigma_-$ from Subroutine 2, line 3. The same applies to the value of $\sigma_-$. Also, in this lemma, the proof uses $\sigma_-\le \sigma_-^2$ in the last inequality, but that is not clarified. From the value of $\sigma_-$ in Subroutine 2, line 3, this is not clear unless the assumption $2M\epsilon\ge 1+2\theta$ is made.}

            \resp{Thanks for the question. We did not use $\sigma_-\leq \sigma_-^2$, and we have added clarification in the paper.}

      \item \comm{Lemma 4.2, Page 16, line 13. Typo: it should be $y_k(\sigma_k)$. The same applies to $a_k(\sigma_k)$.}

      \item \comm{Lemma 4.2, Page 16, line 20. Please also mention that $A_{k+1}=A_k+a_k$ follows from Algorithm 2.}

      \item \comm{Lemma 4.2, Page 16, line 23. In the first inequality, the term $2\gamma A_k(f(x_k)-f^\ast)$ is added to the right-hand side. Please clarify this step.}

      \item \comm{Lemma 4.2, Page 16, line 29. For the second inequality, the proof uses (2.7). However, to use (2.7), one needs $\mu\ge M\|d\|$. From (4.3), $\|d_k\|\ge \eta\sigma_k/M$, and it is not clear how the required condition holds. Please provide more details.}

      \item \comm{Lemma 4.2, Page 16, line 30. The proof uses ``Because $\sigma_k\ge M\|d_k\|$.'' Here the proof is using the fact that $\mu_k=\sigma_k+\lambda_k$, with $\lambda_k=0$ since the argument is in Subroutine 2. This is the same assumption as the previous point, namely $\mu_k\ge M\|d_k\|$, but the proof does not explain why it holds.}

      \item \comm{Lemma 4.2. Even if it is technical, I would prefer to see how the term
                  $\gamma^2 a_k^2-\frac{\gamma A_{k+1}}{\theta\sigma_k}$
                  is eliminated in line 32.}

      \item \comm{Lemma 4.2. Please provide more details on how (4.5) is derived, since the statement ``Iterating the above inequality gives (4.5)'' is not enough.}

      \item \comm{Theorem 4.1. Please provide a proof, or mention that the proof follows the same strategy as Nesterov [47, Theorem 4.3.2].}

      \item \comm{Proof of Lemma 2.3, Page 20, lines 28, 31, and 34. Typos: $\|\nabla f(x+d)\|$ should be used instead of $\|f(x+d)\|$.}

      \item \comm{Proof of Lemma 2.3. The proof implicitly assumes $M\ge 1$, but this is not mentioned in the paper. For example, Assumption 2.1 assumes $M>0$, but for the proof to work, it needs $M\ge 1$. The second inequality is in fact based on $\mu\ge \sqrt{M}\|d\|$, rather than $\mu\ge M\|d\|$. The same applies to line 28. It should be $\frac{3}{4}M\|d\|^4$ instead of $\frac{3}{4}M^2\|d\|^4$, unless one assumes $1\le M\le M^2$ and hence $-\frac{M}{4}\|d\|^4\ge -\frac{M^2}{4}\|d\|^4$. This needs to be fixed and it affects other lemmas, including Lemma 3.3 and others. The fix is to assume $M\ge 1$, so one can use $\mu\ge M\|d\|\ge \sqrt{M}\|d\|$ for the first part, and for the second part use
                  $-\frac{M}{4}\|d\|^4\ge -\frac{M^2}{4}\|d\|^4$.}

            \resp{Thank you for looking into this. The second inequality is based on that
                  \begin{equation*}
                        M^2\|d\|^2 \leq \mu^2, \text{and thus } M^2\|d\|^4\leq \mu^2\|d\|^2.
                  \end{equation*}
                  The same applies to line 28
                  \begin{equation*}
                        4M\|d\| \langle \nabla f(x+d),-d \rangle \geq_{(a)} 2\mu \langle \nabla f(x+d),-d \rangle \geq \|\nabla f(x+d)\|^2 +\frac{3}{4}\mu^2 \|d\|^2\geq_{(b)}  \|\nabla f(x+d)\|^2 +\frac{3}{4} M^2 \|d\|^4,
                  \end{equation*}
                  where $(a)$ is from $\mu \leq 2M\|d\|$, $(b)$ is from $\mu \geq M\|d\|$.
            }

      \item \comm{Proof of Lemma 3.8, Page 21, line 30. There is a typo: the third line is because of $\mu_u>\xi$ instead of $\mu_+>\xi$.}

      \item \comm{Proof of Lemma 3.9. For the equality on line 49, please also refer to Lemma B.1 for the computation of $r'(\xi)$.}

      \item \comm{Proof of Lemma 3.9. There are issues with the second and third inequalities. For example, based on Lemma B.1, the second inequality should involve
                  $\|(\nabla^2 f(y)+\xi I)^{-1}\nabla f(y)\|^3$.
                  Also, the transition from
                  $\sum_{i=1}^n \frac{\beta_i}{(\lambda_i+\xi)^3}$
                  to
                  $\sum_{i=1}^n \frac{\beta_i}{(\lambda_i+\xi)^2}$
                  in order to replace
                  $\sum_{i=1}^n \frac{\beta_i}{(\lambda_i+\xi)^2}$
                  by $\|(\nabla^2 f(y)+\xi I)^{-1}\nabla f(y)\|$ is not properly done.}

            \resp{We have now rewrote the proof accrording to your comment.}

      \item \comm{Proof of Lemma 3.9, Page 22, line 24. Please refer to Subroutine 1, line 16, for the starting value of $r_+$. Although $r_+$ decreases during bisection, the starting value of $r_+$ gives an upper bound for the bisection-complexity analysis.}

      \item \comm{Proof of Lemma 3.9, Page 22, line 30. Please refer to Algorithm 1, line 9, for the starting value of $\mu_+$. Also, there is a typo: $\mu_+=\frac{\sqrt{2M}}{2}\|\nabla f(y_k)\|^{1/2}$.}

      \item \comm{Proof of Lemma 3.9, Page 22, line 16. There is a calculation mistake. Plugging in the inequality from line 30, with the typo above fixed, gives a different bound, namely $\frac{1}{8M^2\|d\|^3}$.}

      \item \comm{Proof of Lemma 3.9, line 20. Please add details explaining how this inequality was derived.}

      \item \comm{Proof of Lemma 3.13, Page 22, line 54. Please add details explaining how the second inequality holds.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 5. Please add details explaining how the inequality follows from
                  $k\ge \frac{3^{4/3}M\|x_0-x^\ast\|}{2\nu}$.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 12. Please add a reference to using (3.1) for the second inequality.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 12. Please add a reference to using (3.2) and (3.3) for the equality.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 14. Please add a reference to Algorithm 1, line 15, for the update of $v_k$.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 19. Please add details explaining why
                  $\frac{1}{2\kappa_h}\|\nabla f(x_k)\|^2\le f(x_k)-f(x^\ast)$
                  holds.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 25. Please add details for the first equality, namely why
                  $\|s_k\|=
                        \left\|\sum_{i=1}^k \frac{i(i+1)}{2}\nabla f(x_i)\right\|$.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 41. Please add that this step uses Assumption 2.3.}

      \item \comm{Proof of Lemma 3.13, Page 23, line 46. Typo in (B.4): it should be $\frac{2\nu^2}{9\kappa_h M}$.}

      \item \comm{Lemma B.2 and its proof, Page 24, line 14. The definition $\eta_0=Ca_0$ is not the same as the definition of $\eta_0$ under Corollary 3.2, equation (3.5). Please clarify.}

            \resp{We have rewrote the proof.}

      \item \comm{Lemma B.2 and its proof, Page 24, line 30. First, it is not clear how $w\le w^{-2}$ gives $\ln(1/w)\ge 2$. Also, in line 30, the proof uses $\ln(1/w)\le 2$ for the inequality to hold.}

            \resp{Thank you for pointing this out. We have refined our proof.}

      \item \comm{Proof of Lemma 4.3, Page 24, line 45. For $\sigma_i a_i^2=A_i+a_i$, please add that this follows from (4.2).}

      \item \comm{Lemma C.2. Please add more details explaining how (C.8) was derived.}

      \item \comm{Lemma C.3, Page 28, line 5. There is a minor calculation mistake in the computation of the derivative. It should be $4A$ instead of $2A$. This affects the final bound in the lemma.}

            \resp{Thank. We have revised it and the corresponding bound.}

      \item \comm{Lemma C.5. There is a typo in the definition of $C(G_0,M_0,M,\epsilon)$; I think there is an extra $M$. Please also recompute the bound on lines 10--12. I think there is a minor computation mistake: the first term should be $(1+2\theta)^3$ instead of $(1+2\theta)^{3/2}$, and $\eta^2$ instead of $\eta$; also, for the fourth term, it should be $(1+2\theta)^2$ instead of $(1+2\theta)$, and there should be $\eta^{3/2}$ in the denominator.}

            \resp{Thanks. We have recomputed the bound as you suggested and added more details to the proof.}
\end{itemize}

\paragraph{Algorithm}
\begin{itemize}
      \item \comm{Subroutine 1, Local Detection (LD), lines 2--4. Can you link it to the results in Corollary 3.1 when describing the algorithm on Page 6, lines 40--53, where $\lambda_k=0$ triggers the LD subroutine?}

            \resp{We now added some discussion in the description of the algorithm.}

      \item \comm{Subroutine 1, Local Detection (LD), line 20. Can you comment on why TR+ is called with $\sigma=0$, i.e., $\operatorname{TR}^+(y,0,r)$?}

            \resp{This is because acceleration requires $\frac{\mu}{\|d\|} = \Theta(1)$. At this stage, we have already identified the bracketing points for the bisection procedure, so the remaining task is only to adjust the radius. Therefore, it suffices to call $\operatorname{TR}^+(y,0,r)$ with $\sigma=0$.}

      \item \comm{Subroutine 2, Ratio Bracketing and Bisection (R\&B) for Algorithm 2. There are typos in line 5: $y$ and $d$ are not defined. They should probably be $y(\sigma_-)$ and $d_-$.}

            \resp{Thanks. We have corrected it.}

      \item \comm{Subroutine 2. There are typos: the condition $\theta>1$ should be the same as in Algorithm 2. The same applies to $0<\eta<1$.}

            \resp{Thanks. We have fixed it.}
\end{itemize}

\paragraph{Numerical Experiments}
\begin{itemize}
      \item \comm{In the Contribution section, Page 3, line 28, the paper refers to [42] and states: ``On a global scale, all accelerated SOM, including ours and [42, 46].'' However, the plots do not show the performance of running [42]. Please either remove that statement or add the results of running this method.}

            \resp{Thanks. We have narrowed down the reference to [46] after careful consideration. The main reason to exclude [42] in the numerical experiments is that the original MS method (A-NPE) [42] paired with the searching procedure (Section 7 of [42]) turns out to be incompetent in practice (also see the discussion in Section 4.3.3 of [47]).
                  In fact, the MS method is more of an algorithmic framework \citep{carmon2022optimal} with many possible choices of second-order oracles, each of which needs a separate searching procedure to meet the required condition to justify the iteration complexity. \\
                  For a specific MS-type method to be practical, we need highly non-trivial enhancements, for example, those in \citep{carmon2022optimal,jiang2020unified} for the cubic regularization oracle. However, these enhancements also bring additional ingredients to the original A-NPE, such as adaptive searching of the Lipschitz constant, warm-start for the searching procedure, etc.  \\
                  Due to space constraints, the sophistication of the enhancements makes it difficult to fairly compare it with other methods in the current numerical experiments. Further exploitation and ablation studies seem to stray away from our main motivation that focuses on the possibility of accelerating trust-region-type methods.
                  For the purpose of the paper, we decide not to exploit these possibilities for the sake of clarity. We believe that the performance evaluation of the MS-type methods with different second-order oracles (including the $\trp$ oracle) itself forms a valuable contribution to the optimization community and will be a topic of our future work.
            }

      \item \comm{Please provide a link to the Git source code. This will help others use the method and compare against it.}

            \resp{Thanks for the suggestion. We have added a link to our current implementation under long-term maintenance: \url{https://github.com/bzhangcw/UTR.jl}.}

      \item \comm{In the plots, the paper uses ATR and ATR (MS), but these two notations are never introduced. I think ATR and ATR (MS) refer to Algorithm 1 and Algorithm 2, but it would be easier to define these, especially for readers who skim the paper and check the plots directly.}

            \resp{Thanks for this suggestion. We have changed the legend names to match the algorithm names.}

      \item \comm{I recommend adding one line to quickly explain the difference between the datasets, for example the size of each one, $N$, or the ratio of both classes. The motivation behind running all algorithms on these different datasets is currently unclear.}

            \resp{Thanks for this suggestion. We add a sentence to explain the difference between the datasets. Each row of presented figures share the sparsity and dimension but different sample size.}

      \item \comm{Please provide extra details on the $\epsilon$ value used and the $\theta$ and $\eta$ parameter values used for Algorithm 2.}

            \resp{Thanks for this suggestion. In the implementation, $\eta = 0.3$, $\theta = 1.3$, and $\epsilon_g$ is the precision parameter (also see the next comment).}

      \item \comm{Please provide extra details on the computation of $D_0$ and $G_0$ in the implementation of Algorithm 2, since these quantities are required for Subroutine 2. For example, how did you compute $x^\ast$?}
            \resp{Thanks for this suggestion. Note that in Algorithm 2, we only use $D_0$ and $G_0$ to set $\sigma_-$ and $\sigma_+$.
                  These values only form a safe interval for $\sigma \in [\sigma_-, \sigma_+]$ to handle the search, and the actual values of $\sigma_-$ and $\sigma_+$ can be determined without actually computing $x^\ast$. }
      \item[] {\color{blue} For example, we can set a $\sigma_-$ that is smaller than $\sqrt{\tfrac{2M\epsilon_g}{1+2\theta}}$. While for $\sigma_+$, it is set according to $G_0$ (the maximum gradient norm) because in the analysis of Lemma 4.5, we used argument such that $\|\nabla f(y(\sigma_+))\| \le G_0$. Thus, it only needs a safe constant value to bound the gradient norm from above along the iterates. As long as the search can terminate successfully, it implies that the choice $\sigma_-, \sigma_+$ is valid.}
\end{itemize}

\subsection{Minor concerns}
\begin{itemize}
      \item \comm{I think you can mention in the abstract that this work is only for unconstrained convex optimization.}

            \resp{Thanks. We now mention in the abstract that this work focuses on unconstrained convex optimization.}

      \item \comm{Page 1, line 55. ``needed to find an $\epsilon$-approximate solution.'' $\epsilon$ was not defined yet, and it would be better to add a sentence mentioning that $\epsilon$ represents the gradient termination tolerance, for example.}

            \resp{Thanks. We now removed the notion ``$\epsilon$-approximate'' in the introduction.}

      \item \comm{Lemma 2.3, Page 4, line 50. Typo: ``hold, holds'' should be ``hold''.}

            \resp{Thanks. We have corrected this typo.}

      \item \comm{Lemma 3.14, Page 13, line 21. Typo: ``holds'' should be ``hold''.}

            \resp{Thanks. We have corrected this typo.}

      \item \comm{In Section 4, please replace $a_k$ with $a_k(\sigma_k)$, since this is how $a_k(\sigma_k)$ is defined in Section 4.2, Page 14, line 19. The same applies to $y_k(\sigma_k)$ instead of $y_k$, as defined in (4.1).}

            \resp{Thanks. We have replaced $y_k$ with $y_k(\sigma_k)$ in Section 4 and add definition of $a_k$ at line 7 of Algorithm 2.}

      \item \comm{Proof of Lemma 3.9. For clarity, please move the definition of $\xi\in[\mu_l,\mu_u]$ to line 45 instead of line 46. For example, one can write: Using $\xi\in[\mu_l,\mu_u]$ and applying the mean value theorem to $r_y(\mu_l)-r_y(\mu_u)$, we have \ldots}

            \resp{Thanks. We have revised the proof as suggested.}

      \item \comm{Proof of Lemma 4.3, Page 24, line 43. Please refer to Algorithm 2, line 9.}

            \resp{Thanks. We have added the reference to Algorithm 2, line 9.}

      \item \comm{Proof of Lemma 4.3, Page 25, line 11. Typo: there should be a factor of $6$ when taking the derivative of the Lagrangian. This factor cancels out at the end, and the final result holds.}

            \resp{Thanks. We have corrected the derivative by adding the missing factor of $6$.}

      \item \comm{Lemma C.2. There is a typo in (C.4). It should be $\delta$ instead of $r$.}

            \resp{Thanks. We have corrected this typo.}

      \item \comm{Proof of Lemma 4.7. Please add ``using (2.4)'' to line 49.}

            \resp{Thanks. We have added ``using (2.4)'' as suggested.}
\end{itemize}